---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  message = FALSE,
  warning = FALSE
)
```

# sormasmap

<!-- badges: start -->
<!-- badges: end -->

`sormasmap` is an R package with the goal to visualize the current spread of the [SORMAS app](http://www.sormas.org) within Germany. The package is primarily used for generating and embedding `leaflet` and `ggplot` graphs. Contributions highly welcome.

## Installation

You can install the released version of sormasmap with:

``` r
devtools::install_github("gstephan/sormasmap")
```

## Geo code and zip code of all German Gesundheitsaemter

One of the primary key features is an overview of all German Gesundheitsaemter. The data is generated from the [RKI PLZ Tool](https://tools.rki.de/plztool/) with its [data source](https://www.rki.de/DE/Content/Infekt/IfSG/Software/software_node.html). This data has all German Gesundheitsaemter in it with all associated ZIP codes. Data is exctracted from the xml file.

Attached to this data are the geo locations with its longitude and latitude for visualization purposes. The geo location is received via the `ggmap` interface to google maps. Package documentation for the setup can be seen [here](https://github.com/dkahle/ggmap).

The data is nested, implicating that some google maps data variables and RKI PLZ tool variables are nested and they can be explored via the e.g. `tidyr`s `unnest()` functions.

```{r example}
library(sormasmap)
gesundheitsaemter
```

As an example, you are interested in one region, here the Thuringian city Eisenach. Select important variables:

```{r select}
library(dplyr)
library(tidyr)

gesus <- gesundheitsaemter %>% 
  select(name, postalcode, plz_rki, gemeinden, long, lat) 
gesus

```

Subset your data:

```{r subset}
eisenach_gesu <- gesus %>% 
  unnest(gemeinden) %>% 
  filter(grepl("Eisenach", gemeinden))
eisenach_gesu
```

Unnest all possilbe Zip code ranges of the Gesundheitsamt that the city Eisenach is associated with:

```{r print}
eisenach_gesu %>% 
  filter(grepl("Wartburgkreis", name)) %>% 
  unnest(plz_rki) %>% 
  print(n = 30)
```

This information prepares the visualization.

## Map of all German Gesundheitsaemter

```{r setup}
library(ggplot2)
library(raster)
```

Get German Bundesland map data

```{r eval=FALSE}
germany <- getData(country = "Germany", level = 1)
```

```{r echo=FALSE}
raster_file <- system.file("extdata", "gadm36_DEU_1_sp.rds", package = "sormasmap")
germany <- readRDS(raster_file)
```

Plot the data:

```{r map}
gesundheitsaemter %>%
  ggplot(aes(long, lat)) +
  geom_polygon(
    data = germany,
    aes(long, lat, group = group),
    colour = "white",
    fill = "#add8e6") +
  geom_point() +
  coord_map() +
  theme_void() +
  labs(title = "German Gesundheitsaemter")
```

